\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2015-03-08 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
updated the manual

In case you successfully ran the configuration script, you are also
ready to compile the internal mesher. This is an alternative to CUBIT
for the mesh generation of relatively simple geological models. The
mesher is no longer dedicated to Southern California and more flexiblity
is provided in this version of the package.

@@

Input for the mesh generation program is provided through the parameter
file \texttt{Mesh\_Par\_file}, which resides in the subdirectory \texttt{DATA/meshfem3D\_files/}.
Before running the mesher, a number of parameters need to be set in
the \texttt{Mesh\_Par\_file}. This requires a basic understanding
of how the SEM is implemented, and we encourage you to read \citet{KoVi98,KoTr99}
and \citet{KoLiTrSuStSh04}.

>>>>

In case you successfully ran the configuration script, you are also
ready to compile the internal mesher. This is an alternative to CUBIT
for the mesh generation of relatively simple models.

@@

Input for the mesh generation program is provided through the parameter
file \texttt{Mesh\_Par\_file}, which resides in the subdirectory \texttt{DATA/meshfem3D\_files/}.
(to see how to use it, see the EXAMPLES specific to the internal mesher in directory \texttt{EXAMPLES/meshfem3D\_examples/}.
Before running the mesher, a number of parameters need to be set in
the \texttt{Mesh\_Par\_file}. This requires a basic understanding
of how the SEM is implemented, and we encourage you to read \citet{KoVi98,KoTr99}
and \citet{KoLiTrSuStSh04}.
